Title here

### 2017-07-07 portfolio/text/ms.Rmd
Clean up a couple variability risk words in the introductory paragraph

\dropcap{I}t can be difficult for individuals to sustain a livelihood from
natural resource extraction. These livelihoods tend to have high annual 
variability in income relative to other professions [@mishra2002; @sethi2012b]. 
In addition to economic risk, such as changes in demand or prices, individuals 
dependent on natural resources are also subject to biological and environmental 
variability [@smith1986]. For example, drought and flooding are a major source 
of risk for agricultural food security and farmers' incomes [@gregory2005], and 
catastrophic disease outbreaks and wildfires increase risk for the logging 
industry [@kirilenko2007].
<!-- Could add anthropogenic perturbations (e.g., Exxon Valdez) to this
list or in the next paragraph. -->

>>>>

\dropcap{I}t can be difficult for individuals to sustain a livelihood from
natural resource extraction. These livelihoods tend to have high annual
variability in income relative to other professions [@mishra2002; @sethi2012b].
In addition to income variability from economic sources,
such as changes in demand or prices, individuals
dependent on natural resources are also subject to biological and environmental
variability [@smith1986]. For example, drought and flooding are a major source
of risk for agricultural food security and farmers' incomes [@gregory2005], and
catastrophic disease outbreaks and wildfires increase risk for the logging
industry [@kirilenko2007].
<!-- Could add anthropogenic perturbations (e.g., Exxon Valdez) to this
list or in the next paragraph. -->
